Hypertension and microbiome

### 2019-01-02 rrbiome.Rmd
Minor

```{r Reading maaslins output}
maas.results.df.signf <- read.table("maaslin/maaslin_merged_phfinrisk_genus.txt", header=TRUE, sep='\t') %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
           Beta = Coefficient) %>%
   dplyr::filter(Qval < 0.05)

@@

```{r maaslin significant table}
maas.results.df.signf %>%
    select(Name, Feature, Beta, Qval) %>%
    kable           
```

>>>>

```{r Reading maaslins output}
maas.results.df.signf <- read.table("maaslin/maaslin_merged_phfinrisk_genus.txt", header=TRUE, sep='\t') %>%
    merge(names.dset %>% select(Covariate, Category, Name), by.x ="Variable", by.y = "Covariate") %>%
    dplyr::mutate(Qval = p.adjust(P.value, method="BH"),
           beta = Coefficient) %>%
   dplyr::filter(Qval < 0.05)

@@

```{r maaslin significant table}
maas.results.df.signf %>%
    select(Name, Feature, beta, Qval) %>%
    kable           
```
